ABM simulating short-term mating behaviors

### 2022-05-30 submission/manuscript.tex
edits in writing

Gender differences in short-term mating behaviors are well-documented in
human sexuality research. Existing studies usually conflate gender
differences in mating preferences with differences in sexual behaviors,
which is theoretically problematic. Using an agent-based model, we
investigated the circumstances under which heterosexual and homosexual
men and women's differential preferences for short-term mating would
result in gender differences in short-term mating behaviors. The model
showed that when all individuals in a closed heterosexual population
were considered, men and women had the same average number of short-term
mating experiences and short-term mates even when men had stronger
preferences for short-term mating. Men (vs.~women) had a higher average
number of both experiences and mates only when heterosexual men and
women in the mating pool (i.e., those with a non-zero number of
short-term mating experiences) were considered. Moreover, when men had
stronger preferences for short-term mating than women, gay men had a
higher average number of both experiences and mates compared to both
lesbian women and heterosexual men. These results suggest that
theoretically speaking, even when gender differences in mating
preferences existed, those in short-term mating behaviors only occurred
among particular populations, or when men's preferences for short-term
mating are not constrained by those of women. Suggestions for future
research in human mating psychology and behaviors were provided.

@@

Gender differences in sexual behaviors, especially short-term mating
behaviors, are well-documented in human sexuality research. For example,
research has found that heterosexual men, as compared to heterosexual
women, have a higher average number of past short-term sexual partners
(Oliver \& Hyde, 1993; Petersen \& Hyde, 2010; Rissel et al., 2014), and
engage in both short-term mating and extramarital sex more often
(Petersen \& Hyde, 2010). These gender differences have also been
observed between gay men and lesbian women (Bailey et al., 1994; Bryant
\& Demian, 1994; Peplau et al., 1997, 2004).

@@

Intuitive as this line of reasoning is, there are good reasons to doubt
its soundness. This is because any heterosexual sexual encounter
involves both a man and a woman (the frequency of encounters involving
more than two persons is negligible, e.g., Herbenick et al., 2017). A
new short-term mating experience for a man is, therefore, also a new
experience for a woman, and the same logic applies to counting a new
short-term mate. As a result, the psychological differences in
short-term mating preferences may not result in behavioral ones in the
heterosexual case (Archer, 2019).

As a starting point, we took gender differences in mating preferences as
conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993) and
repeatedly supported by empirical investigations (e.g., Schmitt, 2003;
Walter et al., 2020). Using an agent-based model, we investigated
whether men and women's differential preferences for short-term mating
would result in gender differences in short-term mating behaviors, and
if so, then under what conditions they would result in differences in
the number of short-term mating experiences and short-term mates.

@@

As for mating standards, men are less selective in accepting someone as
a potential short-term mate. For example, studies using U.S. college
samples have found that the minimum percentile ranks that men found
acceptable for a potential short-term sexual partner were lower than
those accepted by women, both in terms of overall desirability and
individual traits (e.g., social status, attractiveness) (Kenrick et al.,
1990; Regan, 1998). Another study also found that when presented with
identical descriptions of potential mates, men on average rated them as
more desirable than women did (Wiederman \& Dubois, 1998).

Some evidence shows that gender differences in mating preferences also
existed between gay men and lesbian women. A survey study using a
community sample from the U.S. found that gay men were more interested
in short-term mating than lesbian women were, and that this gender
difference was comparable to that existing among heterosexual
individuals (Bailey et al., 1994). An additional indirect piece of
evidence on differential standards for short-term mates comes from a
recent study finding that significantly more gay men than lesbian women
reported to have accepted a casual sexual offer from a same-gender
person (Matsick et al., 2021). Past studies suggest that the gender
difference in the acceptance rate of casual sexual offers may originate
from men and women's differential standards for short-term mates (Conley
et al., 2011; Hald \& Høgh-Olesen, 2010). Thus, as a postulation, gay
men may also have lower standards than lesbian women for short-term
mates.

@@

Since heterosexual sex in most cases involves one man and one woman,
men's relatively high interest in short-term mating can be constrained
by women's preference for long-term relationships (Archer, 2019; Symons,
1979). This is because men's short-term mating preferences -- with the
relatively rare exception of sexual violence -- can only translate into
behaviors when there are women willing to have sex with them. When a new
short-term mating encounter occurs, it counts both towards men's total
number of short-term mating encounters as well as towards women's.
Similarly, a new short-term mate counts towards both men and women's
total number of short-term mates. Therefore, the total number of
short-term mating experiences and short-term mates must be equal between
heterosexual men and women at the population level. However, it is
important to note that although heterosexual men's total number of
short-term mating is equal to that of women, this does not necessarily
mean that the total number of men and women who have ever had short-term
mating must be equal. It is possible that there is a smaller proportion
of men (vs.~the proportion of women) who contribute to the total number
of short-term mating. Following this line of reasoning, we would expect
to observe no gender difference in short-term mating behaviors among
heterosexual individuals even when there are gender differences in
mating preferences.

@@

By using a spatial agent-based model, the present study investigated
whether men and women's differential preferences for short-term mating
would result in gender differences in short-term mating behaviors, and
if they did, under what circumstances. Preferences for short-term mating
were operationally defined as the likelihood of engaging in short-term
mating when encountering a mate as well as the standards for short-term
mates (Buss \& Schmitt, 1993). Short-term mating behaviors were
operationally defined as the number of short-term mating experiences and
the number of past short-term mates (Petersen \& Hyde, 2010).

We modeled this process among both heterosexual individuals and gay men
and lesbian women to examine whether constraints set by the opposite
sex's preferences would affect short-term mating behaviors. Individuals'
sexual orientation was conceptualized in terms of behaviors only in our
model. Heterosexual men had short-term mating or formed a long-term
relationship only with women, while gay men only with other men, and
mutatis mutandis for women.

@@

Gay men engaged in short-term mating behaviors more than heterosexual
men did (Figure 2). The average number of short-term mating experiences
was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) =
-134.87, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.81. Similarly,
the average number of short-term mates was higher among gay men
(\emph{M} = 1.72, \emph{SD} = 0.19) than among heterosexual men
(\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) = -206.91, \emph{p}
\textless{} .001, Cohen's \emph{d} = 5.85.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. Statistics were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
\end{figure}

@@

\caption{\label{tab:table_1}\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model}}
\centering
\begin{threeparttable}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2in}llllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\makecell[c]{Average short-term mating\\experiences (in-pool)}} & \multicolumn{5}{c}{\makecell[c]{Average short-term\\mates (in-pool)}} \\
\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-11}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10}
\multicolumn{1}{c}{\em{ }} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}}\\
\midrule
Same likelihood*Same standard & 2.21 & 0.38 & 2.20 & 0.37 & 0.03 & 1.39 & 0.12 & 1.39 & 0.12 & 0.04\\
Same likelihood*Different standard & 2.82 & 0.36 & 2.21 & 0.28 & 1.89 & 1.76 & 0.15 & 1.38 & 0.09 & 3.13\\
Different likelihood*Same standard & 2.80 & 0.48 & 2.78 & 0.47 & 0.03 & 1.57 & 0.14 & 1.56 & 0.14 & 0.05\\
Different likelihood*Different standard & 3.78 & 0.50 & 2.79 & 0.35 & 2.31 & 2.12 & 0.17 & 1.56 & 0.11 & 3.84\\
\bottomrule
\end{tabular}}
\begin{tablenotes}
\small
\item \textit{Note.} The statistics were calculated with subsamples of men and women who had had engaged in short-term mating behaviors. See Supplementary Materials for the mean and standard deviation of sample sizes.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

Moreover, gender differences in short-term mating behaviors emerged when
heterosexual men and women had different mating standards, but not when
they had different short-term mating likelihood. When women had a higher
standard than men did, less men than women in the population were above
a potential partner's standard and thus had a chance to have sex with
them. This contributed to the unequal number of men and women in the
mating pool, which led to gender differences in short-term mating
behaviors among this population.

In the light of these results, previous empirical observations of gender
differences in short-term mating behaviors among heterosexual
individuals (e.g., Petersen \& Hyde, 2010) appear perplexing (e.g.,
Gurman, 1989). Possible explanations for these empirical results that
seem illogical considering the simulation findings may have to do with
features of the observation process. One possibility is sampling bias in
the observations (e.g., Wiederman \& Dubois, 1998) since surveys
regarding short-term mating behaviors may tend to attract individuals
who already engage in such behaviors. Another possibility is that
heterosexual men and women tend to report short-term mating behaviors
differently. This difference may be a result of social desirability bias
(Alexander \& Fisher, 2003) or due to men and women's different
estimation strategies (e.g., men tend to round up) (Brown \& Sinclair,
1999).

@@

Using agent-based modeling, the present study simulated the
circumstances under which men and women's differential preferences for
short-term mating resulted in gender differences in short-term mating
behaviors. We found when men (vs.~women) had a stronger preferences for
short-term mating, heterosexual men and women engaged in short-term
mating behaviors to the same extent, while gay men engaged in more
short-term mating behaviors as compared to lesbian women. Gay men
engaged in more short-term mating behaviors than heterosexual men did.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-alexander_truth_2003}{}}%
Alexander, M. G., \& Fisher, T. D. (2003). Truth and consequences: Using
the bogus pipeline to examine sex differences in self‐reported
sexuality. \emph{The Journal of Sex Research}, \emph{40}(1), 27--35.
\url{https://doi.org/10.1080/00224490309552164}

\leavevmode\vadjust pre{\hypertarget{ref-archer_reality_2019}{}}%
Archer, J. (2019). The reality and evolutionary significance of human
psychological sex differences. \emph{Biological Reviews}, \emph{94}(4),
1381--1415. \url{https://doi.org/10.1111/brv.12507}

@@

@@

>>>>

Gender differences in short-term mating behaviors are well-documented in
human sexuality research. Existing studies usually conflate gender
differences in mating preferences with differences in sexual behaviors,
which is theoretically problematic. Using an agent-based model, we
investigated the circumstances under which heterosexual and homosexual
men and women's differential preferences for short-term mating would
result in gender differences in short-term mating behaviors. The model
showed that when all individuals in a closed heterosexual population
were considered, men and women had the same average number of short-term
mating experiences and short-term mates even when men had stronger
preferences for short-term mating. Men (vs.~women) had a higher average
number of both experiences and mates only when heterosexual men and
women who successfully participated in the mating pool (i.e., those with
a non-zero number of short-term mating experiences) were considered.
Moreover, when men (vs.~women) had stronger preferences for short-term
mating, gay men had a higher average number of both experiences and
mates compared to both lesbian women and heterosexual men. These results
suggest that theoretically speaking, even when gender differences in
mating preferences exist, those in short-term mating behaviors only
occur among particular populations, or when men's preferences for
short-term mating are not constrained by those of women. Suggestions for
future research in human mating psychology and behaviors were provided.

@@

Gender differences in sexual behaviors, especially short-term mating
behaviors, are well-documented in human sexuality research. For example,
research has found that heterosexual men, as compared to heterosexual
women, report to have a higher average number of past short-term sexual
partners (Oliver \& Hyde, 1993; Petersen \& Hyde, 2010; Rissel et al.,
2014), and engage in both short-term mating and extramarital sex more
often (Petersen \& Hyde, 2010). These gender differences have also been
observed between gay men and lesbian women (Bailey et al., 1994; Bryant
\& Demian, 1994; Peplau et al., 1997, 2004).

@@

Intuitive as this line of reasoning is, there are good reasons to doubt
its soundness. This is because any heterosexual sexual encounter
involves both a man and a woman (the frequency of encounters involving
more than two persons is negligible, e.g., Herbenick et al., 2017). A
new short-term mating experience for a man is, therefore, also a new
experience for a woman. Likewise, when a man has a new short-term mate,
so does his partner. As a result, the psychological differences in
short-term mating preferences may not result in behavioral ones in the
heterosexual case (Archer, 2019).

As a starting point, we took gender differences in mating preferences as
conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993),
which is repeatedly supported by empirical investigations (e.g.,
Schmitt, 2003; Walter et al., 2020). Using an agent-based model, we
investigated whether men and women's differential preferences for
short-term mating would result in gender differences in short-term
mating behaviors, and if so, then under what conditions they would
result in differences in the number of short-term mating experiences and
short-term mates.

@@

As for mating standards, men are less selective in accepting someone as
a potential short-term mate. For example, studies using U.S. college
samples have found that the minimum percentile ranks of the desirability
of a potential short-term sexual partner accepted by men were lower than
those accepted by women, in terms of both the overall desirability and
the desirability of individual traits (e.g., social status,
attractiveness) (Kenrick et al., 1990; Regan, 1998). Another study also
found that when presented with identical descriptions of potential
mates, men on average rated them as more desirable than women did
(Wiederman \& Dubois, 1998).

Some evidence shows that gender differences in mating preferences also
exist between gay men and lesbian women, suggesting that these
differences are based on individuals' gender rather than their sexual
orientation. A survey study using a community sample from the U.S. found
that gay men were more interested in short-term mating than lesbian
women were, and that this gender difference was comparable to that
existing among heterosexual individuals (Bailey et al., 1994). An
additional indirect piece of evidence on differential standards for
short-term mates comes from a recent study finding that significantly
more gay men than lesbian women reported to have accepted a casual
sexual offer from a same-gender person (Matsick et al., 2021). Past
studies suggest that the gender difference in the acceptance rate of
casual sexual offers may originate from men and women's differential
standards for short-term mates (Conley et al., 2011; Hald \&
Høgh-Olesen, 2010). Thus, as a postulation, gay men may also have lower
standards than lesbian women for short-term mates.

@@

Since heterosexual sex in most cases involves one man and one woman,
men's relatively high interest in short-term mating can be constrained
by women's preference for long-term relationships (Archer, 2019; Symons,
1979). This is because men's short-term mating preferences -- with the
exception of sexual violence -- can only translate into behaviors when
there are women willing to have sex with them. When a new short-term
mating encounter occurs, it counts towards both men's total number of
short-term mating encounters as well as women's, and both men and women
have new short-term mates. Therefore, the total number of short-term
mating experiences and short-term mates must be equal between
heterosexual men and women at the population level. However, it is
important to note that although heterosexual men's total number of
short-term mating is equal to that of women, this does not necessarily
mean that the total number of men and women who have ever had short-term
mating must be equal. It is possible that there is a smaller proportion
of men (vs.~the proportion of women) who contribute to the total number
of short-term mating. Following this line of reasoning, we would expect
to observe no gender difference in short-term mating behaviors among
heterosexual individuals even when there are gender differences in
mating preferences.

@@

By using a spatial agent-based model, the present study investigated
whether men and women's differential preferences for short-term mating
would result in gender differences in short-term mating behaviors, and
if they did, under what circumstances. Preferences for short-term mating
were operationally defined as the likelihood of engaging in short-term
mating upon encountering a mate and the standards for short-term mates
(Buss \& Schmitt, 1993). Short-term mating behaviors were operationally
defined as the number of short-term mating experiences and the number of
past short-term mates (Petersen \& Hyde, 2010).

We also modeled forming long-term relationships as a background process.
A pair of individuals had a possibility to commit to a long-term
relationship upon meeting each other. We modeled forming long-term
relationships as a behavioral outcome and ignored the psychological
processes behind it, although we recognize gender differences may also
exist in long-term mating strategy (Buss \& Schmitt, 1993).

We modeled these processes among both heterosexual individuals and gay
men and lesbian women to examine whether constraints set by the opposite
sex's preferences would affect short-term mating behaviors. Individuals'
sexual orientation was conceptualized in terms of behaviors only in our
model. Heterosexual men had short-term mating or formed a long-term
relationship only with women, while gay men only with other men, and
mutatis mutandis for women.

@@

Gay men engaged in short-term mating behaviors more than heterosexual
men did (Figure 2). The average number of short-term mating experiences
(as calculated using the full population of men) was higher among gay
men (\emph{M} = 2.63, \emph{SD} = 0.37) than among heterosexual men
(\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) = -134.87, \emph{p}
\textless{} .001, Cohen's \emph{d} = 3.81. Similarly, the average number
of short-term mates (as calculated using the full population of men) was
higher among gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among
heterosexual men (\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) =
-206.91, \emph{p} \textless{} .001, Cohen's \emph{d} = 5.85.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
\end{figure}

@@

\caption{\label{tab:table_1}\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model}}
\centering
\begin{threeparttable}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2in}llllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\makecell[c]{Average short-term mating\\experiences (in-pool)}} & \multicolumn{5}{c}{\makecell[c]{Average short-term\\mates (in-pool)}} \\
\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-11}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10}
\multicolumn{1}{c}{\em{ }} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}}\\
\midrule
Same likelihood*Same standard & 2.21 & 0.38 & 2.20 & 0.37 & 0.03 & 1.39 & 0.12 & 1.39 & 0.12 & 0.04\\
Same likelihood*Different standard & 2.82 & 0.36 & 2.21 & 0.28 & 1.89 & 1.76 & 0.15 & 1.38 & 0.09 & 3.13\\
Different likelihood*Same standard & 2.80 & 0.48 & 2.78 & 0.47 & 0.03 & 1.57 & 0.14 & 1.56 & 0.14 & 0.05\\
Different likelihood*Different standard & 3.78 & 0.50 & 2.79 & 0.35 & 2.31 & 2.12 & 0.17 & 1.56 & 0.11 & 3.84\\
\bottomrule
\end{tabular}}
\begin{tablenotes}
\small
\item \textit{Note.} The averages were calculated with subsamples of men and women who had had engaged in short-term mating behaviors. See Supplementary Materials for the mean and standard deviation of sample sizes.
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

Moreover, gender differences in short-term mating behaviors emerged when
heterosexual men and women had different mating standards, but not when
they had different short-term mating likelihood. When women had a higher
standard than men did, less men than women in the population were above
a potential partner's standard and thus had a chance to have sex with
them. This contributed to the unequal number of men and women in the
mating pool, which led to gender differences in short-term mating
behaviors among this population. In comparison, even when men and women
had different short-term mating likelihood, the probability of any pair
of them ending up having sex is the product of their individual
likelihood (since men and women made decisions independently). As this
probability is the same for both parties, the gender difference in
short-term mating likelihood did not translate into different behaviors.

In the light of these results, previous empirical observations of gender
differences in short-term mating behaviors among heterosexual
individuals (e.g., Petersen \& Hyde, 2010) appear perplexing (e.g.,
Gurman, 1989). Possible explanations for these empirical results that
seem illogical considering the simulation findings may have to do with
features of the observation process. One possibility is sampling bias in
the observations (e.g., Wiederman \& Dubois, 1998) since surveys
regarding short-term mating behaviors may tend to attract individuals
who already engage in such behaviors. Our results suggest that when this
group of individuals is considered, there can be gender differences in
short-term mating behaviors that do not exist in the full population. A
second explanation is that heterosexual men and women's self-reported
sexual behaviors are affected by social desirability bias due to gender
norms. Men may overreport since having more sexual partners can show
their masculinity and yield them reputation benefits, while women may
underreport because this violates the chastity norm (Fisher, 2013). A
third explanation is that men and women have different estimation
strategies of their sexual experiences. Men may tend to approximate and
round up, while women's tendency to count instances may lead to lower
estimations (Brown \& Sinclair, 1999; Mitchell et al., 2019).

@@

Using agent-based modeling to simulate short-term mating behaviors, we
found when men (vs.~women) had a stronger preferences for short-term
mating, heterosexual men and women engaged in short-term mating
behaviors to the same extent, while gay men engaged in more short-term
mating behaviors as compared to lesbian women. Gay men engaged in more
short-term mating behaviors than heterosexual men did.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-archer_reality_2019}{}}%
Archer, J. (2019). The reality and evolutionary significance of human
psychological sex differences. \emph{Biological Reviews}, \emph{94}(4),
1381--1415. \url{https://doi.org/10.1111/brv.12507}

@@

\leavevmode\vadjust pre{\hypertarget{ref-fisher2013gender}{}}%
Fisher, T. D. (2013). Gender roles and pressure to be truthful: The
bogus pipeline modifies gender differences in sexual but not non-sexual
behavior. \emph{Sex Roles}, \emph{68}(7), 401--414.

@@

\leavevmode\vadjust pre{\hypertarget{ref-mitchell_why_2019}{}}%
Mitchell, K. R., Mercer, C. H., Prah, P., Clifton, S., Tanton, C.,
Wellings, K., \& Copas, A. (2019). Why do men report more opposite-sex
sexual partners than women? Analysis of the gender discrepancy in a
british national probability survey. \emph{The Journal of Sex Research},
\emph{56}(1), 1--8. \url{https://doi.org/10.1080/00224499.2018.1481193}
